title

### 2024-10-16 index.qmd
push to docs/ and add notebooks

---
title: title
authors:
  - name: Norah Jones
    affiliation: The University
    roles: writing
    corresponding: true
bibliography: references.bib
---

>>>>

---
title: title
shorttitle: A Short title # aog-article-pdf
shortauthors: Isaiah      # aog-article-pdf
authors:
  - name: Isaiah Espinoza
    email: gespinoz@umd.edu
    roles: author
    affiliation:
      - name: University of Maryland
        department: Department of Government and Politics
        city: College Park
        state: MD
        country: US
reference-section-title: References
date: "2024-10-16"
---
